---
title: "Figure 3"
output:
  html_document:
    code_folding: hide
    fig_height: 5
    fig_width: 7
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
pathname = here::here()
library(magrittr)
library(knitr)
library(dplyr)
library(ggplot2)
library(ggbeeswarm)
library(beeswarm)
library(ggthemes)
library(viridis)
library(lme4)
library(schoRsch)
library(DHARMa)
library(multcomp)
library(tidyr)
library(rstanarm)
library(ggrepel)
library(rstan)
library(rstanarm)
library(MASS)
devtools::install_github("mikeod38/dauergut")
library(dauergut)
library(plotly)


dauer_ANOVA <- . %>% lm(data = ., formula = pct ~ genotype)
```

#__*daf-28*, but not *daf-7*, is strongly reduced by temperature__{.tabset}

##3A

```{r daf7 temp data}
strains = "N2"
#strains<-c("N2","ft7")
days<-c("11_23_16", "12_6_16")
#days <- "11_23_16" # 12_6 was likely L2s based on the timing

d7GFP<-read.csv(file.path(pathname, "extdata/2A_3A_daf7GFP.csv")) %>%
  filter(mean!=4095 & genotype %in% strains & date %in% days & pheromone == 0 & food == "OP50") %>%
  mutate(genotype = factor(genotype, levels=strains), ID = as.character(ID)) %>%
  separate(ID, c("ID.A", "ID.B"), sep = ":", extra = "drop") %>% 
  mutate(genoID = as.factor(paste(date, genotype, ID.A, sep = ":")), cell.norm = mean)

df <- d7GFP %>% group_by(genotype, date, neuron, temp, genoID) %>% summarise(cell.norm = mean(cell.norm))

#plot
p<-df %>% ggplot(aes(x=temp, y=cell.norm)) +
  list(add.scatter(),add.median(width = .5),add.quartiles()) + 
  labs(
  title = "daf-7 expression does not decrease at high temperatures",
  x = "temperature (ยบC)",
  y = "mean intensity") +
  stat_smooth(method="lm",linetype="dashed", size = 0.2, colour = "grey", alpha = 0.05) +
  add.n() +
  theme_classic() + 
  theme(axis.title.x = element_text(size=16),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 15),
        strip.text.x = element_text(size=20))
p

library(lsmeans)
log.tran<-make.tran(type="genlog", param = c(0.5,10))
lm.ASI.lin <- with(log.tran, lm(linkfun(cell.norm) ~ temp, data = df))
```

**Figure 3A**
_daf-7_ expression does not strongly decrease at high temperatures. Quantification of _daf-7p::gfp_ fluorescence in the ASI,neurons in L1 larvae grown at the indicated temperatures. Each data point is the average GFP fluorescence of a single animal (2 neurons per animal); numbers in parentheses below indicate the total number of animals examined. Horizontal lines are the median; error bars are quartiles. Dashed lines indicate slope of linear regression as a function of temperature. 


```{r d7 model results}
library(sjPlot)
sjt.lm(lm.ASI.lin, depvar.labels = "log(GFP expression)", show.fstat = TRUE)
```

##3B

```{r daf-28 temp curve}
tempdays<-c("1", "4", "6", "8", "10")
foods <- "OP50"
strains <- "N2"
d28<-read.csv(file.path(pathname,'extdata/2D_3B_4B_daf-28_GFP_rict-1.csv')) %>%
separate(ID, c("ID.A", "ID.B"), sep = ":", extra = "drop") %>%
  subset(pheromone == 0) %>% 
  mutate(day = as.factor(day), genotype = factor(genotype, levels = strains),
         genoID = interaction(date,neuron,temp,genotype,ID.A))

df <- d28 %>% subset(day %in% tempdays & food %in% foods & mean !=4095 & genotype %in% strains) %>% group_by(date,temp,genotype,neuron,genoID) %>% summarise(cell.norm = mean(mean)) %>%
  data.frame() %>% mutate(group.id = interaction(genotype, neuron)) # take mean of each worm

## plot
(p<-df %>% ggplot(aes(x=temp, y=cell.norm)) +
   list(add.scatter(),add.median(width = .5),add.quartiles()) + 
    theme_classic() +
  facet_grid(.~neuron) +
  scale_color_viridis(discrete = TRUE) +
  labs(title = "daf-28 expression is controlled by temperature",
    x = "temperature",
    y = "mean fluorescence",
    colour = "Temperature") + add.n() +
   stat_smooth(method="lm",linetype="dashed", size = 0.2, colour = "grey", alpha = 0.05) +
   theme(axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size= 20),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 15),
        strip.text.x = element_text(size=20),
        panel.spacing.x=unit(2, "lines")))


lm.ASI.lin <- with(log.tran, lm(linkfun(cell.norm) ~ temp, data = subset(df, neuron == "ASI")))
#lm.ASI.poly.2 <- update(lm.ASI.lin, formula = . ~ . - temp + poly(temp,2,raw=TRUE))
#anova(lm.ASI.lin,lm.ASI.poly.2) #quadratic fits better but not enough temp points to model
#anova(lm.ASI.lin)

lm.ASJ.lin <- with(log.tran, lm(linkfun(cell.norm) ~ temp, data = subset(df, neuron == "ASJ")))
#anova(lm.ASJ.lin)

```

**Figure 3B**  
_daf-28_ expression strongly decreases at high temperatures. Quantification of _daf-28p::gfp_ fluorescence in the ASI (left) and ASJ (right) neurons in L1 larvae grown at the indicated temperatures. Each data point is the average GFP fluorescence of a single animal (2 neurons per animal); numbers in parentheses below indicate the total number of animals examined. Horizontal lines are the median; error bars are quartiles. Dashed lines indicate slope of linear regression as a function of temperature. 


```{r d28 model results}
library(sjPlot)
sjt.lm(lm.ASI.lin, lm.ASJ.lin, depvar.labels = c("ASI", "ASJ"), show.fstat = TRUE)
```

##3C

```{r daf7 and daf-28 FISH dataload}
FISH <- read.csv(file.path(pathname, 'extdata', '3C_daf7_28_FISH.csv')) %>%
  separate(Label, c("group","number"), sep = "-") %>%
  mutate(number = case_when(
    is.na(number) ~ "01",
    TRUE ~ number
  )) %>% 
  separate(group, c("measure", "genotype", "probe", "temp", "tube"), sep = "_") %>%
  mutate(animal = interaction(genotype,probe,temp,tube,number))

background <- FISH %>% filter(type == "background") %>% 
  select(animal,Mean) %>%
  rename(Mean.background = Mean)

df <- filter(FISH, type == "cell") %>% 
  left_join(.,background) %>% mutate(cell.norm = Mean - Mean.background)
```


```{r daf7 FISH analysis, results='hide'}
daf7 <- filter(df, probe == "daf7Cy5")

#simple lm
linmod<-lm(data=daf7, formula=cell.norm~temp)
#check for outliers
daf7 <- dauergut::flag_outliers(linmod, daf7, threshold = 4, noplot = TRUE) %>% filter(outlier.status == FALSE)


contrast <- daf7 %$% t.test(cell.norm ~ temp)
contrast <- data.frame(p.value = contrast$p.value) %>% dauergut::prange()
plot.contrasts <- c("",contrast$prange)

#linmod<-lm(data=daf7[daf7$outlier.status == FALSE,], formula=cell.norm~temp)
#Fstat not sig#
fit <- BayesianFirstAid::bayes.t.test(daf7[daf7$temp == "25", "cell.norm"], 
                               daf7[daf7$temp == "27", "cell.norm"])
fit_sum <- fit$stats %>% 
  data.frame() %>% 
  select(mean,q2.5.,q97.5.,q25.,q75.) %>%
  tibble::rownames_to_column('parameter') %>%
  dplyr::filter(., grepl("mu",parameter)) %>%
  dplyr::filter(., !grepl("diff",parameter)) %>%
  rename(lower.CL = q2.5., 
         upper.CL = q97.5.,
         lower.25 = q25.,
         upper.75 = q75.) %>%
  mutate(temp = as.factor(c(25,27)),
         x.pos = c(1.3,2.3))

p <- ggplot(daf7, aes(x=temp)) + #x-layer
    theme_my +
    geom_errorbar(data=fit_sum, aes(x=x.pos,y=mean, ymin=lower.CL, ymax=upper.CL),
                  width=0,colour ="grey", lwd=0.15) + #90% cred int for 95% one-sided H0
    geom_errorbar(data=fit_sum, aes(x=x.pos,y=mean, ymin = lower.25, ymax = upper.75),
                  width=0,colour = "darkgrey", lwd = 0.15+0.7) + #75% cred interval
    geom_segment(data = fit_sum, aes(x = x.pos-0.005*nrow(fit_sum),
                                   y = mean, xend = x.pos+0.005*nrow(fit_sum), 
                                   yend = mean), colour = "darkgrey") + 
    scale_x_discrete(labels=function(x) sub(" ","\n",x,fixed=TRUE)) +
    stat_summary(aes(x=temp, y=800), geom="text", label=plot.contrasts, show.legend = TRUE, size=4) + # pvalues
    theme(axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          axis.line = element_line(size=0.2),
          axis.title = element_text(size=16)) +
  geom_quasirandom(aes(y=cell.norm),colour = "#990000", cex=1,
                           width = 0.02,size=0.3,
                           method = 'smiley') +
          stat_summary(aes(y=cell.norm),fun.y = median, 
                       fun.ymin = function(z) {quantile(z,0.25)}, 
                       fun.ymax = function(z) {quantile(z,0.75)},
                       geom = "errorbar", width = 0.15, lwd = 0.15) +
          stat_summary(aes(y=cell.norm),fun.y = median, 
                       fun.ymin = median, 
                       fun.ymax = median,
                       geom = "crossbar", width = 0.25, lwd = 0.35) +
          labs(y = "normalized expression",x = "temperature")

```

```{r daf7FISH plot}
p
```



##3D

```{r daf28 FISH analysis, results = 'hide'}
daf28 <- filter(df, probe == "daf28Cy5")

#simple lm
linmod<-lm(data=daf28, formula=cell.norm~temp)
#check for outliers
daf28 <- dauergut::flag_outliers(linmod, daf28, threshold = 4, noplot = TRUE) %>%
  filter(outlier.status == FALSE)

contrast <- daf28 %$% t.test(cell.norm ~ temp)
contrast <- data.frame(p.value = contrast$p.value) %>% dauergut::prange()
plot.contrasts <- c("",contrast$prange)

#linmod<-lm(data=daf28[daf28$outlier.status == FALSE,], formula=cell.norm~temp)
#Fstat not sig#
fit <- BayesianFirstAid::bayes.t.test(daf28[daf28$temp == "25", "cell.norm"], 
                               daf28[daf28$temp == "27", "cell.norm"])
fit_sum <- fit$stats %>% 
  data.frame() %>% 
  select(mean,q2.5.,q97.5.,q25.,q75.) %>%
  tibble::rownames_to_column('parameter') %>%
  dplyr::filter(., grepl("mu",parameter)) %>%
  dplyr::filter(., !grepl("diff",parameter)) %>%
  rename(lower.CL = q2.5., 
         upper.CL = q97.5.,
         lower.25 = q25.,
         upper.75 = q75.) %>%
  mutate(temp = as.factor(c(25,27)),
         x.pos = c(1.3,2.3))

p <- ggplot(daf28, aes(x = temp)) + # x-layer
  theme_my +
  geom_errorbar(
    data = fit_sum, aes(x = x.pos, y = mean, ymin = lower.CL, ymax = upper.CL),
    width = 0, colour = "grey", lwd = 0.15
  ) + # 90% cred int for 95% one-sided H0
  geom_errorbar(
    data = fit_sum, aes(x = x.pos, y = mean, ymin = lower.25, ymax = upper.75),
    width = 0, colour = "darkgrey", lwd = 0.15 + 0.7
  ) + # 75% cred interval
  geom_segment(data = fit_sum, aes(
    x = x.pos - 0.005 * nrow(fit_sum),
    y = mean, xend = x.pos + 0.005 * nrow(fit_sum),
    yend = mean
  ), colour = "darkgrey") +
  scale_x_discrete(labels = function(x) sub(" ", "\n", x, fixed = TRUE)) +
  coord_cartesian(ylim = c(0,320)) +
  stat_summary(aes(x = temp, y = 300), geom = "text", label = plot.contrasts, show.legend = TRUE, size = 4) + # pvalues
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.line = element_line(size = 0.2),
    axis.title = element_text(size = 16)
  ) +
  geom_quasirandom(
    aes(y = cell.norm), colour = "#990000", cex = 1,
    width = 0.02, size = 0.3,
    method = "smiley"
  ) +
  stat_summary(
    aes(y = cell.norm), fun.y = median,
    fun.ymin = function(z) {
      quantile(z, 0.25)
    },
    fun.ymax = function(z) {
      quantile(z, 0.75)
    },
    geom = "errorbar", width = 0.15, lwd = 0.15
  ) +
  stat_summary(
    aes(y = cell.norm), fun.y = median,
    fun.ymin = median,
    fun.ymax = median,
    geom = "crossbar", width = 0.25, lwd = 0.35
  ) +
  labs(y = "normalized expression", x = "temperature")

```

```{r plot daf28FISH}
p
```


##3E-F
```{r daf-28GFP rict-1 25v27, results='hide', fig.keep='all'}
days = as.factor(8:10) # days containing N2 and ft7 27ยบ data
temps = c("25","27")
strains = c("N2", "ft7")
foods = "OP50"
d28<-read.csv(file.path(pathname,'extdata', '2D_3B_4B_daf-28_GFP_rict-1.csv')) %>%
separate(ID, c("ID.A", "ID.B"), sep = ":", extra = "drop") %>%
  subset(mean!=4095 & food == foods &
           temp %in% temps &
           genotype %in% strains &
           pheromone == 0 &
           day %in% days) %>%
  mutate(day = as.factor(day), genotype = factor(genotype, levels = strains),
         genoID = interaction(date,genotype,ID.A), temp = factor(temp, levels = temps))

df <- d28 %>% group_by(date,temp,genotype,neuron,genoID) %>% summarise(cell.norm = mean(mean)) %>%
  data.frame() %>% mutate(group.id = interaction(genotype, temp)) %>% arrange(temp, genotype, neuron) # take mean 

# anova(with(log.tran,lm(linkfun(cell.norm) ~ temp, data = df[df$neuron == "ASI",])),with(log.tran,lm(linkfun(cell.norm) ~ temp+genotype, data = df[df$neuron == "ASI",])))
# # for ASI, F = 4.0071, 1Df p = 0.0481 for genotype
# anova(with(log.tran,lm(linkfun(cell.norm) ~ temp, data = df[df$neuron == "ASJ",])),with(log.tran,lm(linkfun(cell.norm) ~ temp+genotype, data = df[df$neuron == "ASJ",])))
# # for ASJ, F = 38.082, 1Df, p < 0.001 for genotype
# # no significant interaction of temp with genotype for either neuron

lm.ASI <- with(log.tran, lm(linkfun(cell.norm) ~ temp + genotype, data = df[df$neuron == "ASI",]))
lm.ASJ <- with(log.tran, lm(linkfun(cell.norm) ~ temp + genotype, data = df[df$neuron == "ASJ",]))

contrasts.ASI<-summary(lsmeans(lm.ASI, pairwise ~ genotype | temp)$contrasts) %>% dauergut::prange()
contrasts.ASJ<-summary(lsmeans(lm.ASJ, pairwise ~ genotype | temp)$contrasts) %>% dauergut::prange()

stan.ASJ<-with(log.tran, stan_lmer(linkfun(cell.norm) ~ group.id + (1|genoID), data = df[df$neuron == "ASJ",], adapt_delta = 0.99, iter = 4000))

stan.ASI<-with(log.tran, stan_lmer(linkfun(cell.norm) ~ group.id + (1|genoID), data = df[df$neuron == "ASI",], adapt_delta = 0.99, iter = 4000))

mixed.ASI <- stan.ASI %>% getStan_CIs(type = "log", group = "temp", base=10, compare_gt = TRUE)
mixed.ASJ <- stan.ASJ %>% getStan_CIs(type = "log", group = "temp", base=10, compare_gt = TRUE)

labels <- c("WT", "rict-1(ft7)")


#### plot ASI ###
mixed <- mixed.ASI
p1 <- df %>% dplyr::filter(neuron == "ASI") %>% ggplot(aes(x = genotype, y = cell.norm)) + 
  geom_quasirandom(aes(y=cell.norm, pch = temp),colour = "#339900", cex=1,
                           width = 0.075,size=0.3,
                           method = 'smiley') + 
  list(add.median(width=0.25),add.quartiles()) + facet_grid(.~temp) +
  stat_summary(aes(x=as.numeric(as.factor(genotype)) + 0.3, y=0),
                   fun.data = fun_length, geom = "text", size = 3) +
  add.Bayes.CI() +
  coord_cartesian(ylim=c(0,4095)) +
  labs(title = "ASI",
    x = "genotype",
    y = "mean fluorescence (AU)",
    colour = "Temperature") +
   theme_classic() + 
  theme(axis.text.x = element_text(size = 12, face = "italic"),
          axis.text.y = element_text(size = 12),
          axis.line = element_line(size=0.2),
          axis.title = element_text(size=16)) +
  scale_x_discrete(labels = labels) +
  guides(pch=FALSE)

#### plot ASJ ###
mixed<-mixed.ASJ
p2 <- df %>% dplyr::filter(neuron == "ASJ") %>% ggplot(aes(x = genotype, y = cell.norm)) + 
  geom_quasirandom(aes(y=cell.norm, pch = temp),colour = "#339900", cex=1,
                           width = 0.075,size=0.3,
                           method = 'smiley') + 
  list(add.median(width=0.25),add.quartiles()) + facet_grid(.~temp) +
  stat_summary(aes(x=as.numeric(as.factor(genotype)) + 0.3, y=0),
                   fun.data = fun_length, geom = "text", size = 3) +
  add.Bayes.CI() +
  coord_cartesian(ylim=c(0,4095))+
  labs(title = "ASJ",
    x = "genotype",
    y = "mean fluorescence (AU)",
    colour = "Temperature") +
  theme_classic() + 
  theme(axis.text.x = element_text(size = 12, face = "italic"),
          axis.text.y = element_text(size = 12),
          axis.line = element_line(size=0.2),
          axis.title = element_text(size=16)) +
  scale_x_discrete(labels = labels) +
  guides(pch=FALSE)


```

<div style="float: left; width: 425;">

```{r, results = 'markup', eval = TRUE, fig.width = 4, fig.height=5}
p1                                  
```

</div>

<div style="float: left; width: 425;">

```{r, results = 'markup', eval = TRUE, fig.width = 4, fig.height=5}
p2
```

</div>

<div style="float: right; width: 100%;">

**Figure 3C**  
_daf-28_ expression is reduced in _rict-1_ mutants at multiple temperatures. Quantification of _daf-28p::gfp_ fluorescence in the ASI (left) and ASJ (right) neurons in L1 larvae grown at the indicated temperatures. Each data point is the average GFP fluorescence of a single animal (2 neurons per animal); numbers in parentheses below indicate the total number of animals examined. Horizontal lines are the median; error bars are quartiles.  

</div>

```{r d28 rict-1 model results}
library(sjPlot)
sjt.lm(lm.ASI, lm.ASJ, depvar.labels = c("ASI", "ASJ"), show.fstat = TRUE)
```