---
title: "Figure 2"
output:
  html_document:
    code_folding: hide
    fig_height: 5
    fig_width: 7
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
pathname = getwd()
library(magrittr)
library(knitr)
library(dplyr)
library(ggplot2)
library(ggbeeswarm)
library(beeswarm)
library(ggthemes)
library(viridis)
library(lme4)
library(schoRsch)
library(DHARMa)
library(multcomp)
library(tidyr)
library(rstanarm)
library(ggrepel)
library(rstan)
library(rstanarm)
library(MASS)
library(png)
devtools::install_github("mikeod38/dauergut")
library(dauergut)

dauer_ANOVA <- . %>% lm(data = ., formula = pct ~ genotype)
```


#__Figure 2 Intestinal mTORC2 regulates sensory neuron state__{.tabset}

##2A

```{r daf7 data load, warning=FALSE} 
strains<-c("N2","mg360","ft7","ft7_ges1resc")
dates<-c("10_22_16", "11_9_16", "11_23_16") #dropped "12_6_16" due to missingness
d7GFP<-read.csv(file.path(pathname,"extdata/2A_3A_daf7GFP.csv")) %>% filter(mean!=4095 & genotype %in% strains & date %in% dates & temp == "27" & food == "OP50") %>% mutate(genotype = factor(genotype, levels=strains), ID = as.character(ID)) %>%
  separate(ID, c("ID.A", "ID.B"), sep = ":", extra = "drop") %>% 
  mutate(genoID = paste(date, genotype, ID.A, sep = ":"), cell.norm = mean) #genoID is animal, 2 cells per animal measured.

df <- d7GFP %>% group_by(date, genotype, genoID) %>% summarise(cell.norm = mean(cell.norm)) # take mean of each worm

### Linear models ###

log.tran<-lsmeans::make.tran(type="genlog", param = c(0,10))
lmm2<-with(log.tran, lmer(linkfun(cell.norm) ~ genotype + (1|date) + (1|genotype:date), data = df))
lm <- with(log.tran, lm(linkfun(cell.norm) ~ genotype, data = df))
stanlmer <- with(log.tran, rstanarm::stan_lmer(linkfun(cell.norm) ~ genotype + (1|date) + (1:genotype:date), 
                                               data = df, 
                                               chains = 3, 
                                               cores =4, 
                                               seed = 2000,
                                               iter=6000,
                                               control = list(adapt_delta=0.99)))

### compare ft7 to rescue H0, ft7 = ft7_resc ###
rescue.test <- d7GFP %>% subset(genotype %in% c("ft7", "ft7_ges1resc")) %$% with(log.tran, t.test(linkfun(cell.norm) ~ genotype))
rescue.p <- data.frame(p.value = rescue.test$p.value) %>% dauergut::prange()

#H0, all genotypes = N2
contrasts<-dauergut::dunnett_contrasts(lm, ref.index = 1, "genotype")
mixed <- stanlmer %>% getStan_CIs(type = "log", base = 10)

plot.contrasts<-c("",contrasts$prange[1:2],"")
plot.contrasts.2 <- c("", "", "", rescue.p$prange)

p2<-dauergut::plot_CIs(df=df, title='daf-7 expression in ASI at 27ยบ is
controlled by intestinal rict-1', plot.contrasts=plot.contrasts, plot.contrasts.2 = plot.contrasts.2, ypos = 4700, offset = 0, type = "GFP")

img.path <- file.path(pathname,"figures/2A_daf7GFP.png")

```

<div style="float: left; width: 50%;">

``` {r, echo = FALSE, results = 'markup', eval = TRUE}
include_graphics(img.path)                                   
```

</div>

<div style="float: right; width: 50%;">

```{r, echo = TRUE, results = 'markup', eval = TRUE, fig.height=5.5}
p2
```

</div>




<div style="float: right; width: 100%;">
2A. Intesinal _rict-1_ regulates daf7GFP levels in ASI neurons. L1 animals were grown 18hrs post egg lay at 27ยบ. Daf-7::GFP fluorescence quantification shows decreased expression in _rict-1_ mutants. Intestinal expression of _rict-1_ using the intestinal _ges-1_ promoter rescues daf-7::GFP expression. Box and scatter plot show raw data. Bayesian 90% (grey) and 50% (red) credible intervals are shown on the right (see methods). For _rict-1(mg360)_ and _rict-1(ft7)_, `r contrasts$prange[1]` and `r contrasts$prange[2]` compared to N2, respectively. For _ges-1_ rescue, `r rescue.p$prange` compared to _rict-1(ft7)_. n=3 independent experiments.

</div>


```{r 2A daf-7 stats}
knitr::kable(contrasts, caption="Pairwise comparisons from mixed-effects model (Tukey)")
knitr::kable(mixed[,c(6,1:5)], caption = "Bayesian credible intervals")
```


##2B

```{r daf7 FISH, message=FALSE}
daf7FISH<-read.csv("extdata/2B_daf7FISH_4frames.csv") %>%
  separate(Label, c("method","group","sample"),sep = c("-"), extra = "drop") %>%
  separate(sample, c("sample", "type"),sep =":", extra = "drop") %>%
  mutate(genotype = data.frame(do.call(rbind, strsplit(as.vector(group), split = "daf7_mRNA_L1_27d_")))[,2]) %>%
  mutate(ID = interaction(genotype, sample)) %>%
  mutate(genotype = factor(genotype, levels = c("N2", "ft7", "mg360", "mg360resc")))

#measured background fluorescence of each of 4 frames to normalize the sum projection of the neuron
#merge to add mean background value to each row:
background <- filter(daf7FISH, type == "background") %>% dplyr::select(ID, mean)
colnames(background) <- c("ID", "background")

cells<-dplyr::filter(daf7FISH, type == "cell") %>% dplyr::select(ID, sample, mean, genotype)
colnames(cells) <- c("ID", "sample", "cell.mean", "genotype")

daf7FISH <- merge(cells, background,by="ID") %>%
  mutate(cell.norm = cell.mean - mean(background),
         cell.diffnorm = cell.mean - background,
         cell.ratioNorm = cell.mean / background)

#simple lm
lm<-lm(data=daf7FISH, formula=cell.norm~genotype)
#check for outliers
daf7FISH <- dauergut::flag_outliers(lm, daf7FISH, threshold = 4, noplot = TRUE)

lm.0<-lm(data=daf7FISH[daf7FISH$outlier.status == FALSE,], formula=cell.norm~1)
lm.1<-lm(data=daf7FISH[daf7FISH$outlier.status == FALSE,], formula=cell.norm~genotype)
#anova(lm.0, lm.1) p ~ 0.013

stanlm <- stan_glm(cell.norm ~ genotype, data = daf7FISH[daf7FISH$outlier.status == FALSE,])

```

```{r plot daf7FISH}
strains <- levels(daf7FISH$genotype)
contrasts <- dauergut::dunnett_contrasts(lm.1,ref.index = 1,"genotype")
mixed <- stanlm %>% dauergut::getStan_CIs()
rescue.test <- daf7FISH[daf7FISH$outlier.status == FALSE,] %>% subset(genotype %in% c("mg360", "mg360resc")) %$% t.test(cell.norm ~ genotype)
rescue.p <- data.frame(p.value = rescue.test$p.value) %>% dauergut::prange()

plot.contrasts <- c("", contrasts$prange[1:2],"")
plot.contrasts.2 <- c("", "", "", rescue.p$prange)

dauergut::plot_CIs(daf7FISH[daf7FISH$outlier.status == FALSE,], title = "daf7 mRNA is reduced in rict-1 mutants", plot.contrasts = plot.contrasts, plot.contrasts.2 = plot.contrasts.2, ypos = 150, offset = 0, type = "expression")

```

2B.  _Daf-7_ mRNA is reduced in _rict-1_ mutants. Animals were grown 18hrs post egg lay at 27ยบ, then fixed prior to FISH. Intestinal expression of _rict-1_ using the intestinal _ges-1_ promoter rescues _daf-7_ expression. Box and scatter plot show raw data. Bayesian 90% (grey) and 50% (red) credible intervals are shown on the right (see methods). For _rict-1(mg360)_ and _rict-1(ft7)_, `r contrasts$prange[1]` and `r contrasts$prange[2]` compared to N2, respectively. For _ges-1_ rescue, `r rescue.p$prange` compared to _rict-1(ft7)_. n=2 independent experiments, pooled data.
`r nrow(daf7FISH[daf7FISH$outlier.status == TRUE,])` outlier data points were removed in total.

##2C

rescue of rict-1 with daf-7 and daf-28

```{r daf7/daf28 suppress rict-1}
foods <- "OP50"
strains<-c("N2","rict-1(ft7)","rict-1(ft7); ex[ASI::daf7]","rict-1(ft7); ex[ASI::daf28]","rict-1(ft7); ex[ASJ::daf28]")
daf7supp<-read.csv(file.path(pathname, "extdata/2C_daf7_daf28_suppression.csv")) %>% format_dauer(p.dauer = "non")

# daf7supp$genotype<- factor(daf7supp$genotype, levels = strains)
# daf7supp$pct<-as.numeric(paste(daf7supp$dauer/(daf7supp$dauer+daf7supp$pd + daf7supp$non))) #omitted arrest
# daf7supp$non.dauer<-as.numeric(paste(daf7supp$pd+daf7supp$non))

lm <- daf7supp %>% dauer_ANOVA()
#stan
stan.glmm <- daf7supp %>% dauergut::run_dauer_stan()
```

```{r daf7/daf28 suppression plot, fig.width=4}
foods <- "OP50"
contrasts<-dauergut::tukey_contrasts(lm, "genotype")
mixed<-stan.glmm %>% dauergut::getStan_CIs(type = "dauer")
plot.contrasts<-c("",contrasts$prange[1],"","","")
plot.contrasts.2<-c("", "", contrasts$prange[5:7]) #for rescue vs rict-1

(p<-dauergut::plot_CIs(daf7supp, title='daf-7 expression in ASI suppresses rict-1 dauer phenotype', plot.contrasts, plot.contrasts.2, ypos = 1.075, offset = 0, type = "dauer"))
```

##2D

```{r load daf28GFP data}
#days = as.factor(8:10) # days containing N2 and ft7 27ยบ data
days = as.factor(8:10)
strains = c("N2", "ft7")
foods = "OP50"
d28<-read.csv('extdata/2D_3B_daf-28_GFP_rict-1.csv') %>%
separate(ID, c("ID.A", "ID.B"), sep = ":", extra = "drop") %>%
  subset(mean!=4095 & food == foods & temp == "27" & genotype %in% strains & pheromone == 0) %>%
  mutate(day = as.factor(day), genotype = factor(genotype, levels = strains),
         genoID = interaction(date,genotype, ID.A))

df <- d28 %>% subset(day %in% days) %>% group_by(date,genotype,neuron,genoID) %>% summarise(cell.norm = mean(mean)) %>%
  data.frame() %>% mutate(group.id = interaction(genotype, neuron)) # take mean of each worm

```

```{r daf28 rict-1 plot, warning=FALSE, fig.width=8}
#fit simple linmod to est outliers:
log.tran<-lsmeans::make.tran(type="genlog", param = c(0,10)) #make log10 transformation
lm1 <- with(log.tran, lm(linkfun(cell.norm) ~ neuron * genotype, data = df))
df %<>% flag_outliers(lin.mod=lm1, threshold = 4, df = .)

# linear MM
lm <- with(log.tran, lm(linkfun(cell.norm) ~ neuron * genotype, data = df[df$outlier.status==FALSE,]))
stanlmer <- with(log.tran, stan_lmer(linkfun(cell.norm) ~ 1 + group.id + (1|date) + (1:group.id:date), data = df))

with(df[df$neuron == "ASI" & df$outlier.status == FALSE,], with(log.tran, t.test(cell.norm ~genotype)))
with(df[df$neuron == "ASJ" & df$outlier.status == FALSE,], with(log.tran, t.test(cell.norm ~genotype)))


contrasts<-summary(lsmeans::lsmeans(lm, pairwise ~ genotype | neuron)$contrasts) %>% dauergut::prange()
mixed <- stanlmer %>% getStan_CIs(type = "log", group = "neuron", base = 10, compare_gt = TRUE)
plot.contrasts<-c("",contrasts$prange[1],"", contrasts$prange[2])

#### plot ######
p<-(df %>% ggplot(aes(x=genotype, y = cell.norm)) +
  #### plot raw data and quartiles
          geom_quasirandom(aes(y=cell.norm, pch = date),cex=1,colour = "#339900",
                           width = 0.075,size=0.3,
                           method = 'smiley') +
    guides(pch=FALSE) +
    list(dauergut::add.median(width = 0.25), dauergut::add.quartiles()) +
labs(title = "daf-28 is also reduced in rict-1 mutants",
     subtitle = "GFP plot",
           y = "mean GFP intensity", x="genotype") +
  #### plot Bayesian credible intervals
  stat_summary(aes(x=genotype, group = genotype, y = 3500), geom="text", fun.data=box_annot, label=plot.contrasts, size = 6) +
  geom_errorbar(data=mixed, aes(x=x.pos,y=mean, ymin=lower.CL, ymax=upper.CL),
                  width=0,colour ="grey", lwd=0.2) + #90% cred int for 95% one-sided H0
  geom_errorbar(data=mixed, aes(x=x.pos,y=mean, ymin = lower.25, ymax = upper.75),
                  width=0,colour = "darkgrey", lwd = 0.9) + #75% cred interval
      geom_segment(data = mixed, aes(x = x.pos-(0.007*nrow(mixed)), y = mean, xend = x.pos+(0.007*nrow(mixed)), yend = mean), colour = "darkgrey") +
  stat_summary(aes(x=as.numeric(as.factor(genotype)) + 0.3,y=0,group = genotype),
               fun.data = fun_length, geom = "text",size = 4) +
  facet_grid(.~neuron, switch="both") + theme_my +
  theme(axis.text.y = element_text(size=12),
        axis.text.x = element_text(size = 16),
        axis.title = element_text(size=16),
        panel.spacing.x=unit(2,"lines")))

# knitr::kable(summary(lsmeans(lm3, pairwise ~ genotype | neuron, type = "response"))$contrasts)




```

##S1A

```{r daf-16 suppresion}
strains<-c("N2","rict-1(mg360)","rict-1;daf-16")
foods <- "OP50"
daf16supp<-read.csv(file.path(pathname, "extdata/S1A_daf16_suppression.csv")) %>% format_dauer(.,p.dauer = "dauer")

# daf28supp$genotype<- factor(daf28supp$genotype, levels = strains)
# daf28supp$pct<-as.numeric(paste(daf28supp$dauer/(daf28supp$dauer+daf28supp$pd + daf28supp$non))) #omitted arrest
# daf28supp$non.dauer<-as.numeric(paste(daf28supp$pd+daf28supp$non))
lm <- daf16supp %>% dauer_ANOVA()
#stan
stan.glmm <- daf16supp %>% stan_glmer(formula = cbind((dauer+pd), (n-(dauer+pd))) ~ genotype + (1|day) + (1|strainDate) + (1|plateID),
                       data=.,
                       family = binomial(link="logit"),
                       chains = 3, cores =4, seed = 2000,iter=6000,
                       control = list(adapt_delta=0.99))
```

```{r daf-16 suppression plot}
contrasts<-dauergut::tukey_contrasts(lm, "genotype")
mixed<-stan.glmm %>% getStan_CIs(type="dauer")
plot.contrasts<-c("",contrasts$prange[1],"")
plot.contrasts.2<-c("", "", contrasts$prange[3]) #for rescue vs rict-1

(p<-dauergut::plot_CIs(daf16supp, title='rict-1 acts in the insulin pathway to inhibit dauer formation', plot.contrasts, plot.contrasts.2, ypos = 1.075, offset = 0, type = "dauer"))
```

##S1B
```{r rict-1 pheromone response}
strains <- c("N2", "rict-1(ft7)")
foods <- "OP50"
rictC3 <- read.csv(file.path(pathname, 'extdata/S3C_rict1Pheromone.csv')) %>% format_dauer(p.dauer = "exclude") %>% mutate(plateID = interaction(plateID,concentration.uM.))

glm <- glm(data = rictC3, cbind(dauer, non) ~ concentration.uM. * genotype, family = binomial)
glmm <- glmer(data = rictC3, cbind(dauer, non) ~ concentration.uM. + genotype + (1|day/plateID), family = binomial)
brms.glmm <- brms::brm(data = rictC3, formula= dauer | trials(n) ~ concentration.uM. + genotype + (1|plateID), family = binomial)

newdata = data.frame(genotype = rep(strains, each = 241), concentration.uM. = rep(seq(0,2.4, by = 0.01),2),plateID = rep(0, 482), n = rep(60, 482))

predictions <- predict(glm, newdata = newdata, type = "response", se.fit = TRUE)
glmm.predict <- predict(glmm,newdata=newdata,type = "response", re.form = NA) #re.form = ~0)
brms.predict <- predict(brms.glmm,newdata=newdata,type = "response", re.form = NA, allow_new_levels = TRUE)

newdata1 <- cbind(newdata, predictions)
newdata1 %<>% mutate(lower = (fit - se.fit), upper = (fit + se.fit), pct = fit)
newdata2 <- cbind(newdata, glmm.predict) %>% mutate(pct = glmm.predict)
newdata3 <- cbind(newdata, brms.predict) %>% mutate(pct = Estimate/n)
#newdata3 <- effects::effect(newdata, glmm)

#get odds-ratio
mfx::logitor(glm, data = rictC3) # OR ~ 21.3


(p<-rictC3 %>% ggplot(aes(x=concentration.uM.,y = pct)) +
  geom_ribbon(data = newdata1,aes(ymin=lower, ymax=upper,fill=genotype), alpha=0.3) +
  geom_line(data = newdata2,aes(x = concentration.uM., y = pct),colour = "red") +
    geom_line(data = newdata3,aes(x = concentration.uM., y = pct), colour = "green") +
  geom_point(aes(y=pct), size = 0.6, alpha = 0.75, width = 0.05) +
  add.median.dauer() +
  #geom_line(data = newdata2,aes(x = concentration.uM., y = pct), colour = "green") +
  labs(y = "proportion dauer") +
  facet_grid(.~genotype) +
  scale_fill_manual(values = c("grey", "lightblue")) +
  scale_colour_manual(values = c("grey", "lightblue")) +
  geom_text(aes(y = 1.075, x=concentration.uM.), label = "") +
    coord_cartesian(ylim = c(-.005,1.075)) +
      scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1)) +
  theme_my_classic +
  theme(#axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size=16),
        axis.title.y = element_text(size =20),
        strip.text.x = element_blank(),
        panel.spacing = unit(2,"lines")) +
    stat_summary(aes(x=concentration.uM. + 0.3, y=-.025),
                      fun.data = fun_length, geom = "text", size = 4)
)
```
